\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-28 paper/submission.tex
fleshed out intro and biblio
corrected two typos

@@

>>>>

\bibitem{anderson13cell} N.~Anderson, arstechnica, August 29, 2013.

\bibitem{bieber-penn2002} M.~Bieber, Univ.~Penn.~Law Review, 150, 1079 (2002)

@@

\bibitem{pgfw-scn2014} J. Perry, D. Gupta, J. Feigenbaum, and R. Wright,
In: M. Abdalla and R. De Prisco (eds.), $9^{th}$ Conference on Security and 
Cryptography for Networks, September 3-5, 2014, Amalfi, Italy (Springer,
Berlin, 2014)

\bibitem{ay2008} C.~Aggarwal and P.~Yu, In: C.~Aggarwal and P.~Yu (Eds.), 
Privacy-Preserving Data Mining: Models and Algorithms 
(Springer, Berlin, 2008) 11

\bibitem{kamara} S.~Kamara, In: M.~Brenner and M.~Smith (eds.), 
$2^{nd}$ Workshop on Applied Homomorphic Cryptography and Encrypted Computing, 
March 7, 2014, Barbados, West Indies (Springer, Berlin, 2014)

\bibitem{kroll} J.~Kroll, E. Felten, and D. Boneh, Secure protocols for
accountable warrant execution, April 2, 2014,\\
https://freedom-to-tinker.com/blog/felten/\\
secure-protocols-for-accountable-warrant-execution/
